{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-05 Paper/main.tex
Added plots to tex doc with caption Placeholder

>>>>

	\subsection{Curve Estimates for Chosen Specifications}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}

		\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}

		\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_1.pdf}
			\caption{Placeholder}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_2.pdf}
			\caption{Placeholder}
		\end{minipage}
	\end{figure}
